draft 1

### 2015-08-15 finalwriteup/draft.rmd
big dump started regression

![This method was implemented by the British government for a rail project which is still under completion](C:/Users/n9232371/Documents/github/consult/final write up/UKrail.JPG)

@@

- research: dozens of papers using statistical and machine learning to predict project costs
        - construc
        - IT
        - film costs?

        - reference class forecasting - pioneered in british government large gov infrastructure

@@

@@

* K means
* anova
* in construction journals, commonly applied linear regression
* do these acknowledge their data is not normally distributed?

>>>>

![This method was implemented by the British government for a rail project which is still under completion](UKrail.JPG)

@@

previous research:

Given this theory of reference class forecasting was first clearly published in 2003, the idea of predicting project costs from previous data has been the subect of research for many years before that and continues to this day. Although research results have often been promising, industry uptake of the idea is not yet established.

First an overview of the methods used will be presented followed by published theories for the lack of industry uptake.

***need to really do more research on this!!***

A substantial amount of research on project costprediction has been dedicated to the fields of software development and construction projects in particular. These analyses have generally used project information from 15 to 20 large projects. A single dataset may consist of projects from around the world, and each project a different client and project team. The mathematical methods used to predict project costs vary from statistical regressions to deep-learning neural networks. Most studies report neural networks are more accurate than regression

@@

*** ^^^more research^^^ ***

@@

* anova

* linear regression
    * pros

    * cons
        * do these acknowledge their data is not normally distributed?
